Fast and optimal centroiding of faint stars

### 2014-12-31 ms/figure.tex
Update figure.tex

@@

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_psf.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model to the stars and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{4}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_wrongpsf.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from fitting a Gaussian PSF model to the stars and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{5}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_poly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{6}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_spoly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 modified polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{7}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_sdss.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 quartic approximation method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{8}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_psf.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{9}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_wrongpsf.png}
\endminipage
\captionScatter plots showing the relation between error in centroid measurement from fitting a Gaussian PSF model and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{10}
\end{figure}

>>>>

\subsection{7$\times$7 weighted moments}

In addition to the methods mentioned above, we examine weighted moment method which
requires taking a 7$\times$7 patch of image around the brightest pixel,
weighting the pixels by the intensity, and computing the first moments (or center
of mass) of the weighted 7$\times$7 patch thereafter.

@@

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_moment.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement
from the 7$\times$7 weighted moment method and the signal-to-noise ratio of stars,
with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right)
pixels. In each scatter plot, the blue line represents the running median of data points,
and the green line represents CRLB.}\label{4}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_psf.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement
from fitting the exact PSF model to the stars and the signal-to-noise ratio of stars,
with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right)
pixels. In each scatter plot, the blue line represents the running median of data points,
and the green line represents CRLB.}\label{5}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_wrongpsf.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid
measurement from fitting a Gaussian PSF model to the stars and the signal-to-noise
ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left),
and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the
running median of data points, and the green line represents CRLB.}\label{6}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_poly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement
from the 3$\times$3 polynomial method and FWHM of stars, with SNR  of : 5 (upper left),
10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue
line represents the running median of data points, and the green line represents CRLB.}\label{7}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_spoly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement
from the 3$\times$3 modified polynomial method and FWHM of stars, with SNR  of 
: 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each
scatter plot, the blue line represents the running median of data points, and the
green line represents CRLB.}\label{8}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_sdss.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from
the 3$\times$3 quartic approximation method and FWHM of stars, with SNR  of : 5 (upper left),
10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line
represents the running median of data points, and the green line represents CRLB.}\label{9}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_moment.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid
measurement from the 7$\times$7 weighted moment method and FWHM of stars,
with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
In each scatter plot, the blue line represents the running median of data points,
and the green line represents CRLB.}\label{10}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_psf.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement
from fitting the exact PSF model and FWHM of stars, with SNR  of : 5 (upper left),
10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot,
the blue line represents the running median of data points, and the
green line represents CRLB.}\label{11}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_wrongpsf.png}
\endminipage
\captionScatter plots showing the relation between error in centroid measurement
from fitting a Gaussian PSF model and FWHM of stars, with SNR  of : 5 (upper left),
10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the
blue line represents the running median of data points, and the green line represents CRLB.}\label{12}
\end{figure}
